Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/formal.tex
sp
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

However, even non-adversairal schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
\Red{Ale: |when| was not defined, so I changed it to if-then-else}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the |sec| tasks's decision to diverge or not is directly leaked to a
public entitiy.

>>>>

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI.
%
Concretely, consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |pub canFlowTo sec|, but |sec cantFlowTo pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS1 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
\Red{Ale: |when| was not defined, so I changed it to if-then-else}
These two configurations are |pub|-equivalent, but |ic1| will reduce 
(in two steps) 
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straight forward, see Setion~\ref{sec:extensions}.}
then the |sec| tasks's decision to diverge or not is directly leaked to a
public entity.
